A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-07-17 tex/paper.tex
Merged SA intermediate comments and IC 2.4 text

%\vt stands for ``vector theta''
\newcommand{\vt}{ {\bm \theta}}
\newcommand{\vT}{ {\bm \Theta}}
\newcommand{\vg}{\vt_{\star, {\rm grid}}}
\newcommand{\vpp}{\vt_{\star, {\rm post}}}
\newcommand{\finst}{f_{\lambda, {\rm inst}}}
\newcommand{\fsynth}{f_{\lambda, {\rm synth}}}
\newcommand{\vN}{\vt_{\rm N}}
\newcommand{\vtstar}{\vt_{\star}}
\newcommand{\vtcheb}{\vt_{\rm Cheb}}
\newcommand{\vtglobal}{\vt_{\rm global}}
\newcommand{\vtorder}[1]{\vt_{{\rm order}_{#1}}}
\newcommand{\vtorders}{\vt_{\rm orders}}
\newcommand{\vtline}[1]{\vt_{{\rm line}_{#1}}}
\newcommand{\vtlines}{\vt_{\rm lines}}
\newcommand{\vtcov}{\vt_{\rm cov}}
\newcommand{\vM}{\mathsf{M}}
\newcommand{\vD}{\mathsf{D}}
\newcommand{\vR}{\mathsf{R}}
\newcommand{\vC}{\mathsf{C}}
\newcommand{\fM}{ \vec{{\bm M}}}
\newcommand{\fMi}{M_i}
\newcommand{\fD}{ \vec{{\bm D}}}
\newcommand{\fDi}{D_i}
\newcommand{\fR}{ {\bm R}}
\newcommand{\dd}{\,{\rm d}}
\newcommand{\trans}{\mathsf{T}}
\newcommand{\Z}{[{\rm Fe}/{\rm H}]}
\newcommand{\A}{[\alpha/{\rm Fe}]}
\newcommand{\matern}{Mat\'{e}rn}

@@

\newcommand{\vtcheb}{\vt_{\rm Cheb}}
\newcommand{\vtglobal}{\vt_{\rm global}}
\newcommand{\vtorder}[1]{\vt_{{\rm order}_{#1}}}
\newcommand{\vtorders}{\vt_{\rm orders}}
\newcommand{\vtline}[1]{\vt_{{\rm line}_{#1}}}
\newcommand{\vtlines}{\vt_{\rm lines}}
\newcommand{\vtcov}{\vt_{\rm cov}}

@@

\subsection{Exploring the Posterior }
\label{subsec:MCMC}

@@

\begin{figure*}[!htb]
\begin{center}
  \includegraphics[width=5in]{figs/stellar_triangle_Kurucz.png}
  \caption{The posterior probability function of the stellar parameters for WASP-14, an F star, as explored by the MCMC Gibbs sampler. These stellar parameters are marginalized over the Chebyshev ($\vT_{\rm cheb}$) and noise parameters ($\vT_{\rm cov}$). Figure generated with \texttt{triangle.py} \citep{foreman-mackey14}.
}
\label{fig:stellar_posterior}
\end{center}
\end{figure*}

To explore the posterior probability distribution and make inferences on the parameters of 
interest, we employ a hierarchical Monte Carlo Markov Chain (MCMC) approach that nests the standard 
Metropolis-Hastings algorithm (for sampling the parameters $\vt$) inside the Gibbs sampler (which 
rotates through subsets of the hyper-parameters $\vT$).

@@

\begin{deluxetable}{ll}
\tablecaption{Nomenclature used in this document}
\tablehead{
  \colhead{Symbol} & \colhead{Description}
}
\startdata
$i$ & index specifying a pixel\\
$\lambda_i$ & wavelength corresponding to a given pixel $i$\\
$\fundamentalParameters$ & fundamental stellar parameters, $T_{\rm eff}, \log(g), \Z, \A$\\
$\gridParameters$ & stellar parameters that specify a spectrum from a synthetic library\\
$\observationalParameters$ & stellar parameters $v \sin i$, $v_z$, $A_V$, and $R^2/d^2$ that\\
  & are applied during ``post processing'' of the synthetic spectrum\\
$\stellarParameters$ & $\{\fundamentalParameters,\observationalParameters \}$, all stellar parameters\\

>>>>

\newcommand{\vM}{\mathsf{M}}
\newcommand{\vD}{\mathsf{D}}
\newcommand{\vR}{\mathsf{R}}
\newcommand{\vC}{\mathsf{C}}
\newcommand{\fM}{ \vec{{\bm M}}}
\newcommand{\fMi}{M_i}
\newcommand{\fD}{ \vec{{\bm D}}}
\newcommand{\fDi}{D_i}
\newcommand{\fR}{ {\bm R}}
\newcommand{\dd}{\,{\rm d}}
\newcommand{\trans}{\mathsf{T}}
\newcommand{\Z}{[{\rm Fe}/{\rm H}]}
\newcommand{\A}{[\alpha/{\rm Fe}]}
\newcommand{\matern}{Mat\'{e}rn}

@@

@@

@@

\begin{figure*}[!htb]
\begin{center}
  \includegraphics[width=5in]{figs/stellar_triangle_Kurucz.png}
  \caption{The posterior probability function of the stellar parameters for WASP-14, an F star, as explored by the MCMC Gibbs sampler. These stellar parameters are marginalized over the Chebyshev ($\Cheb$) and noise parameters ($\Cov$). Figure generated with \texttt{triangle.py} \citep{foreman-mackey14}.
}
\label{fig:stellar_posterior}
\end{center}
\end{figure*}

@@

\begin{deluxetable}{ll}
\tablecaption{Nomenclature used in this document}
\tablehead{
  \colhead{Symbol} & \colhead{Description}
}
\startdata
$\lambda_i$ & wavelength corresponding to a given pixel $i$\\
$\fundamentalParameters$ & fundamental stellar parameters, $T_{\rm eff}, \log(g), \Z, \A$\\
$\gridParameters$ & stellar parameters that specify a spectrum from a synthetic library\\
$\observationalParameters$ & stellar parameters $v \sin i$, $v_z$, $A_V$, and $R^2/d^2$ that\\
  & are applied during ``post processing'' of the synthetic spectrum\\
$\stellarParameters$ & $\{\fundamentalParameters,\observationalParameters \}$, all stellar parameters\\
